---
title: "gtsummary in quarto"
format: html
execute:
  warning: false
  messages: false
---

```{r}
#| echo: false
library(tidyverse)
library(gtsummary)
nlsy_cols <- c("glasses", "eyesight", "sleep_wkdy", "sleep_wknd", 
               "id", "nsibs", "samp", "race_eth", "sex", "region", 
               "income", "res_1980", "res_2002", "age_bir")
nlsy <- read_csv(here::here("data", "raw", "nlsy.csv"), 
                 na = c("-1", "-2", "-3", "-4", "-5", "-998"),
                 skip = 1, col_names = nlsy_cols) |> 
  mutate(region_cat = factor(region, labels = c("Northeast", "North Central", "South", "West")),
         sex_cat = factor(sex, labels = c("Male", "Female")),
         race_eth_cat = factor(race_eth, labels = c("Hispanic", "Black", "Non-Black, Non-Hispanic")),
         eyesight_cat = factor(eyesight, labels = c("Excellent", "Very good", "Good", "Fair", "Poor")),
         glasses_cat = factor(glasses, labels = c("No", "Yes"))) 
```

# Customization of `tbl_summary()`

```{r}
#| echo: false
tbl_summary(
  nlsy,
  by = sex_cat,
  include = c(sex_cat, race_eth_cat, region_cat,
              eyesight_cat, glasses, age_bir))
```

```{r}
#| echo: false
tbl_summary(
  nlsy,
  by = sex_cat,
  include = c(sex_cat, race_eth_cat, region_cat,
              eyesight_cat, glasses, age_bir),
  label = list(
    race_eth_cat ~ "Race/ethnicity",
    region_cat ~ "Region",
    eyesight_cat ~ "Eyesight",
    glasses ~ "Wears glasses",
    age_bir ~ "Age at first birth"
  ),
  missing_text = "Missing")
```

# Added Code

```{r}
#| error: true
tbl_summary(
  NLSY,
  by = sex_cat,
  include = c(sex_cat, race_eth_cat, region_cat,
              eyesight_cat, glasses, age_bir))
```
*The mistake in the code was that "NSLY" is not an object in our environment, "nsly" is though*

# Corrected Code
```{r}
#| echo: false
#| label: tbl-1
#| tbl-cap: "Table of outcomes by sex"
tbl_summary(
  nlsy,
  by = sex_cat,
  include = c(sex_cat, race_eth_cat, region_cat,
              eyesight_cat, glasses, age_bir))
```
Notice that @tbl-1 is a table
```{r}
#| echo: false
avg_sleep_wknd<- mean(nlsy$sleep_wknd, na.rm=TRUE)
print(avg_sleep_wknd)
```
The average sleep on the weekends is `r avg_sleep_wknd`
The average hours of sleep on the weekends was `r mean(nlsy$sleep_wknd, na.rm=TRUE)`

# Practicing inline_text() function
```{r}
#| eval: true
#| label: tbl-descr
#| tbl-cap: "Descriptive statistics"
table1 <- tbl_summary(
  nlsy,
  by = sex_cat,
  include = c(sex_cat, race_eth_cat, region_cat,
              eyesight_cat, glasses, age_bir, sleep_wknd)) |> 
  add_overall(last = TRUE)
table1
mdn_hrs_sleep<- inline_text(table1, variable = "sleep_wknd", column = "stat_0")

```
The median hours of sleep was `r mdn_hrs_sleep`

